%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%  New template code for TAMU Theses and Dissertations starting Fall 2012.  
%  For more info about this template or the 
%  TAMU LaTeX User's Group, see http://www.howdy.me/.
%
%  Author: Wendy Lynn Turner 
%	 Version 1.0 
%  Last updated 8/5/2012
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                           ACKNOWLEDGEMENTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter*{ACKNOWLEDGEMENTS}
\addcontentsline{toc}{chapter}{ACKNOWLEDGEMENTS}  % Needs to be set to part, so the TOC doesnt add 'CHAPTER ' prefix in the TOC.

It is impossible for me to finish this thesis without the guidance of committee members, help from my friends, all colleagues in PVAMU Cloud Computing Laboratory, and support from my family.

At first, I would like to express my deepest gratitude to my advisor, Dr. Lei Huang, for his professional guidance, giving this chance of doing research in cloud computing area and providing first class environment for our research. I also want to thank Dr. Yang and Dr. Bellam, for they have spent lots of time on reviewing my thesis and have given so many excellent suggestions. Special thanks to Dr. Li, for I had benefited greatly from his outstanding teaching in programming language and algorithms classes and his kindly guidance as graduate program coordinator.

I also would like to say thanks to all colleagues and classmates working in cloud computing lab; Besides technology parts, I have learned a lot things from them about culture in different countries, and our lab has been filled with sweat smell of coffee and happiness everyday. Thank my friend Lulu Shi and her family in special, for they help me settle down when I came to Houston at first time, inviting me have dinner countless times and help our family solve many problems of living and study.

Finally, I want to thank my wife, Sanni Jia and my son, Thomas Yan. Sanni quitted her job and brought our lovely son from China to a totally new world, United States for giving me powerful supports. I could not overcome so many difficulties without them. Thanks to my parent for giving birth and supports to me without asking for any return. Thanks for my sister, Yuqin Yan, for taking all responsibility of caring for my parents that let me worry-free. A.M.D.G.  


\pagebreak{}

\ifx true false
\vspace*{\fill}
\begin{center}
A.M.D.G.
\end{center}
\vspace*{\fill}
\pagebreak{}
\fi
